---
title: "GraphsPrez"
author: "j"
date: "7/3/2018"
output:html_document: 
---




```{r}
library(tidyverse)

```

```{r}

logistic_model <- function(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10){

  # define a vector of time and N THIS IS ODD
  time <- c(0:nsteps)
  N <- numeric(length = length(time))

  #Assign initial population size
  
  N[1] <- N0

  for (t in 1:nsteps) {
    N[t + 1] <- N[t] + (r * N[t] * (1 - (N[t] / K))) - c * N[t]
  }
  # end for loop
  
  #create data frame with sim results
  
  simul <- data.frame(time, N) %>% 
    mutate(C = c * N,
           R = p*C)
  
  
  return(simul)
}
results <- logistic_model()
```






```{r}

logistic_model <- function(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10){

  # define a vector of time and N THIS IS ODD
  time <- c(0:nsteps)
  N <- numeric(length = length(time))

  #Assign initial population size
  
  N[1] <- N0

  for (t in 1:nsteps) {
    N[t + 1] <- N[t] + (r * N[t] * (1 - (N[t] / K))) - c * N[t]
  }
  # end for loop
  
  #create data frame with sim results
  
  simul <- data.frame(time, N) %>% 
    mutate(C = c * N,
           R = p*C)
  
  
  return(simul)
}

```



#Logistic population growth in fisheries. 


#The equation

$$N_{t + 1} = N_t + rN_t(1 - \frac{N_t}{K}) - cN_t$$ 


```{r}
print(results)
```



#The models: C denotes number of catchtes, N denotes population size, and R denotes Revenue.

#What does logistic population growth look like?(little c): 0
#model becomes more complicated as we account for more ecological variables impacting fisheries
```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0, p = 10) %>% 
  gather(variable, value, -time) %>% 
   ggplot(mapping = aes(x = time, y = value)) +
 # geom_line() +
  geom_point(color = "steelblue", size = 2) +
  geom_line() +
  theme_bw() +
  facet_wrap( ~ variable, ncol = 2, scales = "free")
```



#Catch proportion: 0.25
```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.2, p = 10) %>% 
  gather(variable, value, -time) %>% 
   ggplot(mapping = aes(x = time, y = value)) +
 # geom_line() +
  geom_point(color = "steelblue", size = 2) +
  geom_line() +
  theme_bw() +
  facet_wrap( ~ variable, ncol = 2, scales = "free")
```



#catch: 0.5
```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10) %>% 
  gather(variable, value, -time) %>% 
   ggplot(mapping = aes(x = time, y = value)) +
 # geom_line() +
 geom_point(color = "steelblue", size = 1) +
  geom_line() +
  theme_bw() +
  facet_wrap( ~ variable, ncol = 2, scales = "free")
```




#catch 0.9

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = .9, p = 10) %>% 
  gather(variable, value, -time) %>% 
   ggplot(mapping = aes(x = time, y = value)) +
 # geom_line() +
  geom_point(color = "steelblue", size = 1) +
  geom_line() +
  theme_bw() +
  facet_wrap( ~ variable, ncol = 2, scales = "free")
```



#variation in N0
Does not effect K 
Recovery or depletion?

```{r}
logistic_model(r = 1, K = 100, N0 = 75, nsteps = 50, c = .5, p = 10) %>% 
  gather(variable, value, -time) %>% 
   ggplot(mapping = aes(x = time, y = value)) +
 # geom_line() +
  geom_point(color = "steelblue", size = 2) +
  geom_line() +
  theme_bw() +
  facet_wrap( ~ variable, ncol = 2, scales = "free")
```

#variation in R

 
```{r}
logistic_model(r = 2, K = 100, N0 = 75, nsteps = 50, c = .25, p = 10) %>% 
  gather(variable, value, -time) %>% 
   ggplot(mapping = aes(x = time, y = value)) +
 # geom_line() +
  geom_line() +
  theme_bw() +
  facet_wrap( ~ variable, ncol = 2, scales = "free")
```



#Three variables at once. Is size an issue???
```{r}
logistic_model(N0 = 10) %>% 
  ggplot(aes(x = time, y = N, color = C, size = R)) +
  geom_point()
```
#make tranparent
#add lines around outline 





```{r}
logistic_model(r = 2, K = 100, N0 = 75, nsteps = 50, c = .25, p = 10) %>% 
  ggplot(aes(x = time, y = N, color = C, size = R)) +
  geom_point() + 
  geom_line()
```












































