---
title: "My summer paper"
author: "j"
abstract: "Coastal ecosystems are an important source of multiple crucial economic and ecosystem services. As a result, it is important that the health of these ecosystems is maintained in a way that is both sustainable and pragmatic. One pivotal economic service provided by coastal ecosystems is food production. This important service represents the livelihoods of fisher communities around the globe, who are in turn relied upon by billions of people. Simultaneously, large-scale efforts to conserve coastal biodiversity such as the Convention on Biological Diversity call for increased ocean protection, placing further limits on fishing and threatening to constrain food supply. In light of a need for conservation, balancing the livelihoods of fishers and local economies with effective biodiversity maintenance becomes a central conflict. We address this issue at its source by designing a layout for reserve networks. Specifically, we evaluate a variety of different scenarios including changes in population growth rates, harvesting intensities, initial population sizes, and time scales. Based on these results, we provide comprehensive recommendations for management of fisheries."
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    code-folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Coastal ecosystems are an important source of multiple crucial economic and ecosystem services including but not limited to marine ecotourism, high levels of biodiversity, and notably food production. However, these abundant ecosystems are increasingly threatened by overexploitation, coastal development, pollution, and climate change (Halpern et al. 2008). Thus, it is crucial that the biodiversity of these ecosystems is maintained in a way that is both sustainable and pragmatic. In fact, Aichi Biodiversity Target 11 of United Nations Convention of Biodiversity (CBD) calls for the protection of at least 10 percent of coastal and marine areas, especially areas of particular importance for biodiversity and ecosystem services by 2020.

One effective way to preserve marine ecosystems is through the establishment of Marine Protected Areas (MPAs), or areas in which fishing is limited or entirely prohibited. MPAs have been shown to be a highly effective tool of conservation, producing significant increases in density, biomass, organism size, and species richness of the communities within reserve boundaries (Lester et al. 2009). However, the implementation of MPAs comes with economic ramifications in relation to the output of fisheries. Goal 2 of the United Nations Sustainable Development Goals establishes 2030 as a target year to end of hunger and to ensure food access by all people. The ensuing question of whether we can maintain and even improve biodiversity while simultaneously accelerating food production from fisheries is possible becomes central to the global community.

Without effective management, however, both of these crucial goals appear at odds. Unsurprisingly, many countries have been simply rushing to meet their goal of 10% conserved marine area only by stretching the definition of ‘protected’ beyond its breaking point (Sala et al. 2018). It is this apparent conflict that we address with our research, which attempts to pinpoint the “sweet spot” between conservation and economic output. In order to shed light on our query, we seek to create a recommendation geared towards the optimization of fishery management. We approach this problem through a mathematical model of coupled marine protected area - fishery systems. Our approach allows us to model the revenue potential of different MPA placement along the coastline as well as degrees of protection for different MPA parcels. Additionally, we will research ideal policy for the implementation of our suggested setup, which will likely involve a TURF-Reserve approach which has been growing in popularity as a method of managing sustainable fisheries (Afflerbach et al. 2014).

# Methods

At the core of our simulation is a logistic population growth equation that models the lobster population within symmetrical regions surrounding the coastline of Isla Natividad in Baja Mexico (Fig. 1). This discrete growth equation is designed to account for the effects of fishing as well as immigration and emigration of lobsters between parcels wrapped around Isla Natividad (Ovando et al. 2016). The model is given by:	
                              
$$N_{t+1} = N_t + rN_t(1 - \frac{N_t}{K}) - C_t + N_{in} - N_{out}$$

Where: 

- $N_{t+1}$ = population size next time step

- $N_t$ = current population 

- $r$ = growth constant

- $K$ = carrying capacity

- $Ct$ = the amount of lobsters harvested at time $t$ if parcel $i$ is not a marine reserve

- $N_{in}$ = the amount of lobsters immigrating

- $N_{out}$ = the amount of lobsters emigrating
 

**(code that loads coastline, creates map, map)**

We selected lobsters as the target species for multiple reasons. Lobsters are one of the most profitable fisheries in the region, with prices that can go up tp \$ 17.5 USD per kilogram. Additionally, they are important in ther role of mid-level predators, as the prey on sea urchins and control their populations. Importantly, they are also highly mobile  as compared to other invertebrates. Intuitively, if lobsters are able to benefit from a selected marine reserve size of our simulation, organisms with equal or smaller home-ranges will also benefit from these reserves.

To identify the tradeoff between conservation and fishery output, we simulate 900 different scenarios. We test 9 levels of fishing effort ($c$ from 0.1 to 0.9 in 0.1 increments) and percent marine reserve coverages from 1-100%. We parameterize our model using existing literature (Moland et al., 2011) and our knowledge of the marine area around Isla Natividad (Table 1). Each of the 900 simulations are run for 50 years. For each scenario we calculate the Revenue (defined as catches $\times$ price) and total biomass ($N$) for the final time step.

This approach allows us to test all possible combinations of fishing effort and marine reserve coverage and track the associated economic and conservation benefits. Based on the known state of fishing effort (c = 0.6) and current marine reserve coverage (n = 5%) at Isla Natividad, we can therefore evaluate all alternative management strategies that would produce the same economic yield while increasing lobster biomass outside the reserves.


|Parameter|Value|
----------|------
Initial population size (N0) | 10 kg
Carrying Capacity (K) | 100 kg 
Growth Rate (r) | 1.0834
Movement Rate (m) | 0.1
Catch Rate (c) | 0.7

**Include your chunk with the model code here**
```{r}

logistic_model <- function(r = 1.0834, K = 100, N0 = 10, nsteps = 50, c = 0.7, p = 17500, n = 5, m = 0.1){

  # define a vector of time and N THIS IS ODD
  time <- c(0:nsteps)
  N <- matrix(0, ncol = 100, nrow = length(time))
  C <- N

  #Assign initial population size
  
  N[1,] <- N0

#create pointers
  
left_pointer <- c(100, 1:99)
right_pointer <- c(1:99, 100)
  
c_mpa <- rep(c, 100) 
c_mpa [1 : n] <- 0



  #start for loop

  
  for (t in 1:nsteps) {
    
    N_in <- m * (N[t, left_pointer] + N[t, right_pointer])/2
    N_out <- m * N[t,]
    C[t, ] <- c_mpa * N[t, ]
    
    N[t + 1,] <- N[t,] + (r * N[t,] * (1 - (N[t,] / K))) - C[t,] + N_in - N_out
    
  }
  # end for loop
  #create catch data frame

C[t+1,] <- c_mpa * N[t+1,]

catch_df <- data.frame(time, C) %>% 
  magrittr::set_colnames(value = c("time", 1:100)) %>% 
  gather(parcel, C, -time)

  #create data frame with sim results
  
  simul <- data.frame(time, N) %>% 
    magrittr::set_colnames(value = c("time", 1:100)) %>% 
    gather(parcel, N, -time) %>% 
    left_join(catch_df, by = c("time", "parcel")) %>% 
    mutate(R = p*C,
           zone = ifelse(C == 0, "reserve", "fishing"),
           parcel = as.numeric(parcel))

  return(simul)

}
```

# Results

**Include the chunks that create the rainbow graphs here**

# Discussion

# References

**make sure to copy-paste your references here**

Afflerbach, J.C., Lester, S.E., Dougherty, D.T. and Poon, S.E. 2014. A global survey of “TURF-reserves”, Territorial Use Rights for Fisheries coupled with marine reserves. Global Ecology and Conservation 2, pp. 97–106.
 
Halpern, B.S., Walbridge, S., Selkoe, K.A., Kappel, C.V., Micheli, F., D’Agrosa, C., Bruno, J.F., Casey, K.S., Ebert, C., Fox, H.E., Fujita, R., Heinemann, D., Lenihan, H.S., Madin, E.M.P., Perry, M.T., Selig, E.R., Spalding, M., Steneck, R. and Watson, R. 2008. A global map of human impact on marine ecosystems. Science 319(5865), pp. 948–952.
 
Lester, S.E., Halpern, B.S., Grorud-Colvert, K., Lubchenco, J., Ruttenberg, B.I., Gaines, S.D., Airamé, S. and Warner, R.R. 2009. Biological effects within no-take marine reserves: a global synthesis. Marine Ecology Progress Series 384, pp. 33–46.
 
 
 Moland, E., Olsen, E. M., Andvord, K., Knutsen, J. A., & Stenseth, N. C. (2011). Home range of European lobster (Homarus gammarus) in a marine reserve: implications for future reserve design. Canadian Journal of Fisheries and Aquatic Sciences, 68(7), 1197-1210.
 
Sala, E., Lubchenco, J., Grorud-Colvert, K., Novelli, C., Roberts, C. and Sumaila, U.R. 2018. Assessing real progress towards effective ocean protection. Marine Policy 91, pp. 11–13.





