---
title: "Graphsprez2"
author: "j"
date: "7/10/2018"
output: html_document
---


```{r}
library(tidyverse) 
library(cowplot)
 
```



#This is Equation for 1 cell


$$N_{t + 1} = N_{t} + r * N_{t} * (1 - (N_{t} / K)) - C_{t} + N_{in} - N_{out}$$  





#work on carrying capacity explanation, all else is good.



#Code parameters:

#c = movement rate (into your boat)
#n = how many squares (getting rid)
#p = price
#r = growth rate how many make it /
# what if we had partially protected?: marine protect area(marine reserve)
#what if i partially protext: 
#its about the question you are asking


```{r}






logistic_model <- function(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 5, m = 0.2){

  # define a vector of time and N THIS IS ODD
  time <- c(0:nsteps)
  N <- matrix(0, ncol = n, nrow = length(time))
  C <- N

  #Assign initial population size
  
  N[1,] <- N0

#create pointers
  
left_pointer <- c(n, 1:(n-1))
right_pointer <- c(1:(n-1), n)
  
c_mpa <- c(c, c, 0, c, c )

  #start for loop

  
  for (t in 1:nsteps) {
    
    N_out <- m * N[t,]
    N_in <- m * (N_out[left_pointer] + N_out[right_pointer])/2
    C[t, ] <- c_mpa * N[t, ]
    
    N[t + 1,] <- N[t,] + (r * N[t,] * (1 - (N[t,] / K))) - C[t,] + N_in - N_out
    
  }
  # end for loop
  #create catch data frame

catch_df <- data.frame(time, C) %>% 
  gather(parcel, C, -time)

  #create data frame with sim results
  
  simul <- data.frame(time, N) %>% 
    gather(parcel, N, -time) %>% 
    left_join(catch_df, by = c("time", "parcel")) %>% 
    mutate(R = p*C,
           class = ifelse(parcel %in% "X3", "reserve", "fishing"))
  # to change parcels you need to add them into ifelse like "X2" "X4" etc in addition to changing the c_mpa vector
  
  return(simul)
}
```




```{r}
model_with_emim <- logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 5, m = 0.2) %>% 
  ggplot(mapping = aes(x = time, y = N, color = class, group = parcel, size = R, alpha = 0.5)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()

```


```{r}
model_with_emim
```


#This is Equation for 1 cell


$$N_{t + 1} = N_{t} + r * N_{t} * (1 - (N_{t} / K)) - C_{t} + N_{in} - N_{out}$$ 
#work on carrying capacity explanation, all else is good.




