---
title: "model withMPA"
author: "j"
date: "7/9/2018"
output: html_document
---

---




```{r}
library(tidyverse)

```



#n = number of parcels that are reserves



```{r}

logistic_model <- function(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 17500, n = 5, m = 0.2){

  # define a vector of time and N THIS IS ODD
  time <- c(0:nsteps)
  N <- matrix(0, ncol = 100, nrow = length(time))
  C <- N

  #Assign initial population size
  
  N[1,] <- N0

#create pointers
  
left_pointer <- c(100, 1:99)
right_pointer <- c(1:99, 100)
  
c_mpa <- rep(c, 100) 
c_mpa [1 : n] <- 0



  #start for loop

  
  for (t in 1:nsteps) {
    
    N_in <- m * (N[t, left_pointer] + N[t, right_pointer])/2
    N_out <- m * N[t,]
    C[t, ] <- c_mpa * N[t, ]
    
    N[t + 1,] <- N[t,] + (r * N[t,] * (1 - (N[t,] / K))) - C[t,] + N_in - N_out
    
  }
  # end for loop
  #create catch data frame

C[t+1,] <- c_mpa * N[t+1,]

catch_df <- data.frame(time, C) %>% 
  magrittr::set_colnames(value = c("time", 1:100)) %>% 
  gather(parcel, C, -time)

  #create data frame with sim results
  
  simul <- data.frame(time, N) %>% 
    magrittr::set_colnames(value = c("time", 1:100)) %>% 
    gather(parcel, N, -time) %>% 
    left_join(catch_df, by = c("time", "parcel")) %>% 
    mutate(R = p*C,
           zone = ifelse(C == 0, "reserve", "fishing"),
           parcel = as.numeric(parcel))

  return(simul)
}
```




```{r}
logistic_model() %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```



##normal

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 5, m = 0.2) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```


##( n = 10)
## high N0, high m 

```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 10, m = 0.5) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```

## high N_0, low m 


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 10, m = 0.03) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```



## low N_0, high m 

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 10, m = 0.5) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```



## low N0 low m


```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 10, m = 0.03) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```




##NOW LOOKING AT n = 50

 high N_0, high m 

```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.5) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```

## high N_0, low m 


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.03) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```



## low N_0, high m 

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.5) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```



## low N0 low m


```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.03) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```





##NOW LOOKING AT n = 90


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 90, m = 0.5) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```

## high N_0, low m 


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 90, m = 0.03) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```



## low N_0, high m 

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 90, m = 0.5) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```



## low N0 low m


```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 90, m = 0.03) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, group = parcel, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```










##(n = 10)

#high N0 high m


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 10, m = 0.5) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```


##High N0 low m


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 10, m = 0.03) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```

## low N0 high m

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 10, m = 0.5) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```




## low N0 low m

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 10, m = 0.03) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```


##n = 50 

#high N0 high m


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.5) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```


##High N0 low m


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.03) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```

## low N0 high m

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.5) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```




## low N0 low m

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.03) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```

# n = 90

```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 50, m = 0.5) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```


##High N0 low m


```{r}
logistic_model(r = 1, K = 100, N0 = 90, nsteps = 50, c = 0.5, p = 10, n = 90, m = 0.03) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```

## low N0 high m

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 90, m = 0.5) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```




## low N0 low m

```{r}
logistic_model(r = 1, K = 100, N0 = 10, nsteps = 50, c = 0.5, p = 10, n = 90, m = 0.03) %>% 
  group_by(time, zone)  %>% 
  summarise(Ntot = sum(N),
            N = mean(N),
            C = sum(C),
            R = sum(R)) %>% 
  ggplot(mapping = aes(x = time, y = N, color = zone, size = R)) +
  geom_line(size = 1) +
  geom_point() +
  theme_bw()
```






```{r}
logistic_model(n = 90) %>% 
  ggplot(mapping = aes(x = time, y = parcel, fill = N)) +
  geom_raster()
```




N = biomass in kilograms
p = 17.5 $/ton
R = c x p in $
c = catches in kilograms
t = years
K = 100 kg






```{r}

results <- matrix(0, ncol = 4, nrow = 900) %>% 
  magrittr:: set_colnames(value = c( "n", "c", "N", "R")) %>% 
  as.data.frame()

i = 1

for(n in c(1 : 100)) {
  
  for(c in seq(0.1, 0.9, by = 0.1)) {
    
    results_i <- logistic_model(n = n, c = c, N0 = 90) %>% 
      filter(time == 50) %>% 
      group_by(time) %>% 
      summarise(N = sum(N), R = sum(R))
    
    results$n[i] <- n
    results$c[i] <- c
    results$N[i] <- results_i$N
    results$R[i] <- results_i$R
    i = i + 1
  }
}
```


```{r}
ggplot(data = results, aes(x = c, y = n, fill = R, z = R ))  +
  geom_raster(interpolate = T) + 
  geom_contour(color = "black") +
  labs(x = "catch rate", y = "reserve size") +
  scale_fill_viridis_c()
```


```{r}
ggplot(data = results, aes(x = c, y = n, fill = N, z = N ) ) +
  geom_raster(interpolate = T) + 
  geom_contour(color = "black") +
  labs(x = "catch rate", y = "reserve size") +
  scale_fill_viridis_c()
```

#geom_vline
#geom_hline
